BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2013-11-26 tex/3-algorithms.tex
Variations++

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Variations for authors, dates and comments}
% Intro, authors
As is, algorithms \ref{extractionAlgo} and \ref{linearAlgo} will performed poorly for authors and dates extraction and are not suitable for comment extraction. The case of authors is problematic because it is not uncommon to encounter the author's name at several places in a page, leading to several rules with maximum score. The heuristic we use to get around this issue consists in adding a new component in the scores of authors extraction rules: the \emph{tree distance} between the evaluated node and the post content node. This new score component takes advantage of the positioning of post's authors which is often a direct child or shares parent with the post content node.

% Dates, authors
Dates are affected by the same issue of often being duplicated in a page, which is complexified by the inconsistances of format between the dates provided in web feeds and their representation on web pages. Our solution uses the same tree distance score component presented

% Comments

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Variations for authors, dates and comments}
% Intro
As is, algorithms \ref{extractionAlgo} and \ref{linearAlgo} will performed poorly for authors and dates extraction and are not suitable for comment extraction. This subsection presents variations of the general extraction techniques presented before. Due to space constraints, we will only provide the main ideas and omit algorithmic and implementation details.

% Authors
The case of authors is problematic because it is not uncommon to encounter the author's name at several places in a page, leading to several rules with maximum score. The heuristic we use to get around this issue consists in adding a new component in the scores of authors extraction rules: the \emph{tree distance} between the evaluated node and the post content node. This new score component takes advantage of the positioning of post's authors which is often a direct child or shares parent with the post content node.

% Dates, authors
Dates are affected by the same duplication issue, as well as inconsistence of format between web feeds and web pages. Our solution to build date extraction rules extends what we presented before for authors by using multiple \emph{target} strings. For instance, if the feed indicates that a post was published on \stringliteral{2013-12-09}, our algorithm will search for a rule to extract one of \stringliteral{}, \stringliteral{}, \stringliteral{} and so on. We use a list of \TODO{0} target date formats that was empirically built during our experiments. While this list is certainly not exhaustive, our approach using string similarity on multiple target is robust to format changes. We did not took the time to support dates in multiple languages but it would be a straightforward modification.

% Comments
Comments are usually available is separated web feeds, organized by blog post. Similarity to blog feeds, comment feeds have a limited number en entries, and in case of overflow content has to be extracted from the post web page.

### 2013-11-26 tex/4-techniques.tex
Reread it all.
Minor fixes in captions + some of variations subsection.
Variations++

% Motivation
In our specific use case of crawling the blog sphere, we encountered several blogs where data was missed because of the lack of JavaScript interpretation. The most frequent cases where blogs using the Disqus\cite{disqus2013} and LiveFyre\cite{livefyre2013} comment hosting services. These tools are very handy to setup for webmasters because the entire comments infrastructure is externalized and the setup essential comes down to including a JavaScript snippet in the target web page. Both of these services heavily rely on JavaScript to download and display the comments, even providing functionalities such as real-time update of comments there are written by users. Less commonly, some blogs are fully rendered using JavaScript. Concretely, when loading such website the web browser will not receive the page content inside an HTML page, but will instead have to execute a script containing the procedure to download and display the page content. On example can be found on the Blogger platforms which proposes as one of its default templates the \emph{Dynamic Views} \cite{antinharasymiv2011} that use this mechanism.

@@

% Click click scripting
In addition to extracting page after JavaScript execution, we also use some of PhantomJS scripting capabilities. When the number of comments on one page exceeds a certain threshold, both Disqus and LiveFyre only load a subset of them and end the stream of comments with a \emph{Show More Comments} buttons. As part of the page load process we instruct PhantomJS to repeatedly click on this button until all comments are loaded. As you will see in the evaluation section, \TODO{we will see..}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.47\textwidth]{img/scrapy_architecture.png}
  \caption{Overview of the crawler architecture.}
  \label{architecture}
\end{figure}

@@

Our use case has two types of spiders: \emph{NewCrawl} and \emph{UpdateCrawl}, which respectively implement the logic to crawl a new blog and to get updates from a previously crawled blog. After downloading the HTML page, blog posts are packed into Items and sent through the folloing pipeline of operation:
\begin{enumerate}[noitemsep]
  \item Render JavaScript
  \item Extract content
  \item Extract comments
  \item Download images
  \item Propagate resulting records to the Invenio backend
\end{enumerate}
This pipeline design, often called the \emph{pipes and filters pattern}\cite[Chapter Messaging Systems]{hohpe2003}, provides great modularity. Indeed, disabeling JavaScript rendering or plugging in an alternative backend can be done by editing a single configuration line.

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Scalability}
When aiming to work with a large number of inputs, it is crucial that every layer of the system is build to be scalable. Citing the Reactive Manifesto\cite{thereactivemanifesto2013}:

>>>>

% Motivation
In our specific use case of crawling the blog sphere, we encountered several blogs where data was missed because of the lack of JavaScript interpretation. The most frequent cases where blogs using the Disqus\cite{disqus2013} and LiveFyre\cite{livefyre2013} comment hosting services. These tools are very handy to setup for web-masters because the entire comments infrastructure is externalized and the setup essential comes down to including a JavaScript snippet in the target web page. Both of these services heavily rely on JavaScript to download and display the comments, even providing functionalities such as real-time update of comments there are written by users. Less commonly, some blogs are fully rendered using JavaScript. Concretely, when loading such website the web browser will not receive the page content inside an HTML page, but will instead have to execute a script containing the procedure to download and display the page content. On example can be found on the Blogger platforms which proposes as one of its default templates the \emph{Dynamic Views} \cite{antinharasymiv2011} that use this mechanism.

@@

% Click click scripting
In addition to extracting page after JavaScript execution, we also use some of PhantomJS scripting capabilities. When the number of comments on one page exceeds a certain threshold, both Disqus and LiveFyre only load a subset of them and end the stream of comments with a \emph{Show More Comments} buttons. As part of the page load process we instruct PhantomJS to repeatedly click on these buttons until all comments are loaded. Path to Disqus and LiveFyre buttons were manually obtained and are store in a configuration file. This is the only non-generic of the extraction stack which would require human intervention to maintain and extend for other commenting platforms.

@@

\begin{figure}
  \capstart
  \centering
  \includegraphics[width=0.47\textwidth]{img/scrapy_architecture.png}
  \caption{Overview of the crawler architecture.\\\small{(Credit: Pablo Hoffman, Daniel Graña, \cite{scrapy2013})}}
  \label{architecture}
\end{figure}

@@

Our use case has two types of spiders: \emph{NewCrawl} and \emph{UpdateCrawl}, which respectively implement the logic to crawl a new blog and to get updates from a previously crawled blog. After downloading the HTML page, blog posts are packed into Items and sent through the folloing pipeline of operation:
\begin{enumerate}[noitemsep]
  \item Render JavaScript
  \item Extract content
  \item Extract comments
  \item Download images
  \item Propagate resulting records to the Invenio back-end
\end{enumerate}
This pipeline design, often called the \emph{pipes and filters pattern}\cite[Chapter Messaging Systems]{hohpe2003}, provides great modularity. Indeed, disabeling JavaScript rendering or plugging in an alternative back-end can be done by editing a single configuration line.

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Scalability}
When aiming to work with a large number of inputs, it is crucial that every layer of the system is build to be scalable. Citing the Reactive Manifesto \cite{thereactivemanifesto2013}:
